A protocol \& event-sourced database for decentralized user-siloed data

### 2019-09-29 draft.tex
abstract: cleans up
Signed-off-by: andrew <andrew@textile.io>

\begin{abstract}
As the Internet expands, the division between a person's digital and physical existence continues to blur. An emerging issue of concern is that the digital part of a person's life is mainly being captured by apps and stored away from the person's control by the companies building those apps. An alternative, called user-siloed data is one area of research that if implemented successfully, could reverse the flow of value derived from personal data, from apps to users. In this paper, we investigate the data formats, access control, and transfer protocols necessary to build a system for user ownership of large-scale digital datasets. The aim of the proposed system is to help power a new generation of web technologies. Our solution combines a novel use of event sourcing with Interplanetary Linked Data (IPLD) to provide a distributed, scalable, and flexible database solution for decentralized applications.
\end{abstract}

>>>>

\begin{abstract}
As the Internet expands, the division between a person's digital and physical existence continues to blur. An emerging issue of concern is that the digital part of a person's life is being stored away from the person's control by companies behind apps and services on the Internet. An alternative architecture for data on the web, called user-siloed data, aims to reverse the flow of data and its derived value so that users, not apps capture it. In this paper, we investigate the data formats, access control, and transfer protocols necessary to build a system for user ownership of large-scale digital datasets. The proposed system aims to help power a new generation of web technologies. Our solution combines a novel use of event sourcing, Interplanetary Linked Data (IPLD), and access control to provide a distributed, scalable, and flexible database solution for decentralized applications.
\end{abstract}
